Generality in food webs scales with species richness, not latitude

### 2015-05-20 manuscript/latitudepaper.tex
Got citations sorted out, waiting for DBS comments

  %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
  Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
  ecological communities~\citep{Petchey2008,Williams2000,Paine1980} and to understand how that structure relates to environmental variables 
  such as habitat type~\citep{Shurin2006,Briand1983}, primary productivity~\citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate~\citep{Baiser2012,Petchey2010}. The latter
  variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
  climate is more variable at high latitudes~\citep{Field1998}. These variables affect both the resources available and species' 
  metabolisms~\citep{Hechinger2011,OConnor2009,White2009,}, and have been proposed as determinants of the strength of 
  interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
  By modulating interactions between species, latitudinal gradients may also shape food-web structure~\citep{}.
  Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
  latitudinal gradient in species richness, one of the most general and robust patterns in ecology~\citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}.

@@

  The tendency of food-web structure to exhibit scaling relationships with
  species richness has been well-established~\citep{Dunne2004,Riede2010}. As
  species richness in particular is also known to vary systematically over
  latitude~\citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}, intuitively one might suspect that any relationship
  between food-web properties such as generality might be due to the latitudinal
  gradient in species richness. In this dataset, however, we did not find
  overall latitudinal gradients in species richness, links per species, 
  generality, vulnerability, or the proportions of food webs accounted for by 
  basal resources, intermediate consumers, and top predators.

  The lack of a latitudinal gradient in species richness in this dataset contrasts
  strongly with other studies~\citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}. As numbers of species and links included in a food web
  vary strongly with sampling effort as well as with the underlying diversity of the study
  area, it is possible that the lack of latitudinal trends here is a result of researchers
  tending to expend similar amounts of sampling effort across studies. This could result in
  food webs describing species-rich tropical communities omitting more species and links
  than species-poor arctic communities. In addition, it is worth noting that gradients in
  species richness are generally measured for a single taxonomic group at a time (e.g.~\citep{Kaufman1995}).
  It is possible that these taxa are not well-represented in our food webs and that the
  dominant taxa in them do not have an underlying latitudinal gradient in richness. In
  either case, the lack of association between species richness
  and latitude in any ecosystem type nevertheless means that any effect of latitude on scaling relationships
  between species richness and other properties is not being driven by underlying variation in
  species richness, allowing us to more clearly assess effects of latitude on scaling with 
  species richness and proportions of species in different trophic levels.

@@

%\end{spacing}
\newpage
\bibliographystyle{jae}%Compile with jae.bst style file
\bibliography{noISN.bib}% your .bib file(s)

>>>>

  %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
  Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
  ecological communities~\citep{Petchey2008,Williams2000,Paine1966} and to understand how that structure relates to environmental variables 
  such as habitat type~\citep{Shurin2006,Briand1983}, primary productivity~\citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate~\citep{Baiser2012,Petchey2010}. The latter
  variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
  climate is more variable at high latitudes~\citep{Field1998}. These variables affect both the resources available and species' 
  metabolisms~\citep{Hechinger2011,White2011,OConnor2009,White2007}, and have been proposed as determinants of the strength of 
  interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
  By modulating interactions between species, latitudinal gradients may also shape food-web structure.
  Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
  latitudinal gradient in species richness, one of the most general and robust patterns in ecology~\citep{Schemske2009a,Macpherson2002,Kaufman1995}.

@@

  The tendency of food-web structure to exhibit scaling relationships with
  species richness has been well-established~\citep{Dunne2004,Riede2010}. As
  species richness in particular is also known to vary systematically over
  latitude~\citep{Schemske2009a,Macpherson2002,Kaufman1995}, intuitively one might suspect that any relationship
  between food-web properties such as generality might be due to the latitudinal
  gradient in species richness. In this dataset, however, we did not find
  overall latitudinal gradients in species richness, links per species, 
  generality, vulnerability, or the proportions of food webs accounted for by 
  basal resources, intermediate consumers, and top predators.

  The lack of a latitudinal gradient in species richness in this dataset contrasts
  strongly with other studies~\citep{Schemske2009a,Macpherson2002,Kaufman1995}. As numbers of species and links included in a food web
  vary strongly with sampling effort as well as with the underlying diversity of the study
  area, it is possible that the lack of latitudinal trends here is a result of researchers
  tending to expend similar amounts of sampling effort across studies. This could result in
  food webs describing species-rich tropical communities omitting more species and links
  than species-poor arctic communities. In addition, it is worth noting that gradients in
  species richness are generally measured for a single taxonomic group at a time (e.g.~\citep{Kaufman1995}).
  It is possible that these taxa are not well-represented in our food webs and that the
  dominant taxa in them do not have an underlying latitudinal gradient in richness. In
  either case, the lack of association between species richness
  and latitude in any ecosystem type nevertheless means that any effect of latitude on scaling relationships
  between species richness and other properties is not being driven by underlying variation in
  species richness, allowing us to more clearly assess effects of latitude on scaling with 
  species richness and proportions of species in different trophic levels.

@@

%\end{spacing}
\newpage
\bibliographystyle{jae}%Compile with jae.bst style file
\bibliography{noISN}% your .bib file(s)
